### 2016-08-02 Theorem1_FP.tex
edits to theorem 1 and proof

\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $r>1$.}\acnote{Modified.}
\begin{theorem}\label{thm1}
Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q \times r$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
this theorem. Here, $B_1$ and $B_2$, each ask $q \times r$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.
%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
%
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

@@

In $\game{3}(A)$, $r$ random integers are chosen and the $\QryOracle$ oracle sets a $\bad$ flag if query response for any of the $r$ queries is false or any of the $q-r$ queries return true. Also, the hash functions are linear combinations of two random points in $[m]$, similar to $\game{2}(A)$. So, both have equal probability of returning 1.

\begin{equation}
\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
\end{equation}

The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$, except $\game{4}(A)$ outputs 0 if $\bad$ flag is set. In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad =true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive counterpart of $\game{4}(A)$. 
 \tsnote{I have rewritten game $\game{3}(A)$ and added
  $\game{4}(A)$.  It should be that
  $\Prob{\game{2}(A)}=\Prob{\game{3}(A)=1}$. Moreover
  $\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
  \Prob{\game{3}(A)=1}\Prob{\game{3}{A}:\,\neg\bad} =
  \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}$. Finally the event
  $\game{4}(A)=1$ happens iff $\bad \neq \true$.  That means there is
  a non-adaptive adversary that runs~$A$, simulates $\QryOracle$ by
  simply returning 1 iff $c \in \mathcal{I}$, and uses the queries
  with indices in $\mathcal{I}$ as its non-adaptive FPs.  To be
  totally clear, you might want to add a $\game{5}(A)$ that has this
  $\QryOracle$ behavior, and then give the non-adaptive FP-adversary~$A'$ that
simulates~$\game{5}(A)$, and so on. }\fixme{Clean up everything after this.}

\begin{align}
\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
\end{align}

@@

\tsnote{The PRF experiment has not be defined yet, so strictly
  speaking these claims make no sense. }
The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively. When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$. So, 
\begin{align}
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1}\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1}\label{eq:m4}
\end{align}

@@

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.45}{
\hpagess{0.4}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr Func(\univ,[m])$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Ret $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Ret $F_K(x)$\\
Ret $\rho(x)$\\
}
}
\caption{PRF game}\label{fig:prf}
\end{figure}

@@

The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$. $D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.  %\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.  It suffices to say this.}
\noindent
From \Cref{fig:AGame3}, it is evident that
\begin{align}
\Prob{\game{5}(A)=1} &= \Prob{D \, \mbox{outputs $r$ FP} \,}\label{eq:4a}\\
\nonumber \Prob{D \, \mbox{outputs r FP} \,} &=  \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
& \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
\end{align}
\noindent
From \Cref{eq:4a,eq:4b}
\begin{equation}
\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k + O(1/n)]^r \label{eq:4}
\end{equation}

>>>>

\begin{theorem}\label{thm1}
Fix $k,m,n,r>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
For any adversary~$A$ that makes a total of~$q$ queries to its oracle
and has time-complexity~$t$,
there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.
%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
%
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

@@

\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
In $\game{3}(A)$, the hash functions are linear combinations of two random points
in $[m]$, similar to $\game{2}(A)$. 
\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
with lazying sampling in the $\HashOracle$, which is the only place
these random functions are used.  This does not alter the input-output
behavior of the $\HashOracle$.''  Why do we do this?}
We also sample $r$~distinct random integers are chosen \tsnote{why?
  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
flag if query response for any of the $r$ queries is false or any of
the $q-r$ queries return true. \tsnote{We
  set $\bad$ to $\true$ if the queries indexed by the
  set~$\mathcal{I}$ fail to be false-positives, or if any of the
  remaining queries \emph{are} false-positives.  Again, why are we
  doing this?  }

So, both have equal probability of returning 1.  \tsnote{``The value
  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
  conclude that...'' }
\begin{equation}
\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
\end{equation}

The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
except $\game{4}(A)$ outputs 0 if $\bad$ flag is
set.\tsnote{I don't understand this sentence.  What you mean to say is
  something like this: ``By construction, $\game{3}$ and $\game{4}$
  are identical-until-bad.  In addition, $\game{4}$ returning 1
  implies that $\bad$ is never set to~$\true$.  From these two
  observations, we can conclude that $\Prob{\game{4}(A)=1} =
  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
(See my comments below.) Actually it's meaningless, because games are
not not adaptive or non-adaptive.  Adversaries are.}

\tsnote{You need to just justify these next lines better. For example,
why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
\begin{align}
\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
\end{align}
\tsnote{How does the last line follow from the games?  I mean, it
  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
  latter looks at the adversary's output~$\mathcal{Z}$, but the former
ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
equivalent with respect to the events $\game{4}(A)=1$ and
$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
it appears that they have pretty different behaviors. I mean, in
$\game{4}$ the oracle still returns what it is supposed to, even if
$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
no matter if the query is or is not a FP.  You have to explain why
these changes are okay.  Also, why is this new set~$\mathcal{Y}$
necessary?  }
\tsnote{The point that needs to be made about the relationship between
  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
  $\bad=\false$ at the end of the game.  In turn, this implies that
  the game managed to ``guess'', prior to the execution of~$A$, which
  of its queries would result in false-positives.  (By the way, we
  need to state an assumption here: that~$A$ halts and
  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
  reveal~$r$ false positives.  This is without loss of generality; say
why.  I guess you also need to assume that every point in
the~$\mathcal{Z}$ output by~$A$ has already been queried
to~$\QryOracle$.  Strictly speaking this is not without loss of
generality, but would be easily enforced (in the original
  security definitions) by counting as part of the number of
  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
non-adaptive adversary~$D$ that finds~$r$ false positives against
$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
respectively.  (Note, this is \emph{not} the adversary~$D$ that you
give, because the one you give simulates things that it would be given
in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
need for $\game{5}$.)  Now argue that this advantage is upperbounded
by what the theorem claims, i.e. the KM bound raised to~$r$.}

@@

%\tsnote{The PRF experiment has not be defined yet, so strictly
% speaking these claims make no sense. }
The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries
$B_1, B_2$ be as shown in \Cref{fig:BGame1}. \tsnote{Why is $B_2$
  sampling a random function?  This ruins the tightness of security
  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
  of~$\rho_2$.  Also, please use the macro for Func.}  By
construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively. When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$. So, 
\begin{align}
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1}\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1}\label{eq:m4}
\end{align}

@@

%\caption{PRF game}\label{fig:prf}
\begin{figure}
\centering
\fpage{0.45}{
\hpagess{0.4}{0.35}
{
$\experimentv{\ExpPRF{F}{B}}$\\
$K \getsr \calK $\\
$\rho \getsr Func(\univ,[m])$\\
$b \getsr \bits$\\
$b' \getsr B^\calO$\\
Ret $[b = b']$\\
}
{
$\oracle{\calO \smallskip(x)}$\\
if $ b = 1$ then\\
\nudge Ret $F_K(x)$\\
Ret $\rho(x)$\\
}
}
\caption{The PRF experiment for a function family $F \colon \calK
  \times \calX \to [m]$. }\label{fig:prf}
\end{figure}

@@

\tsnote{This proof jumps around too much.  The games should be
  addressed in order, as much as possible.}  
The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and~$D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$. $D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.  %\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.  It suffices to say this.}
\noindent
From \Cref{fig:AGame3}, it is evident that \tsnote{Where is the
  set~$S$ in $D$ and $D'$?  Make sure to give it to~$A$.  Why is this
  extra set~$\mathcal{Y}$ needed?}
\begin{align}
\Prob{\game{5}(A)=1} &= \Prob{D \, \mbox{outputs $r$ FP} \,}\label{eq:4a}\\
\nonumber \Prob{D \, \mbox{outputs r FP} \,} &=  \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
& \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
\end{align}
\tsnote{How does the second line follow?  You're claiming independence
  somehow, but you haven't justified it.}
\noindent
From \Cref{eq:4a,eq:4b}
\begin{equation}
\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k + O(1/n)]^r \label{eq:4}
\end{equation}
